\section{Creating a Character}
PLAYERS are responsible for controlling one or a few characters acting in a game world of shared fiction. The procedure for creating a character is as follows, the PLAYER follow these steps taking note of every decision or discovery along the way:
\begin{enumerate}
  \item {Choose or discover the character's class, taking note of the characters HIT VALUE (i.e. how hard it is for them to be hit) and number of HITS (i.e. how many hits they can take before being taken out);}
  \item {Choose or discover the character's appearence. Each class has a suggested appearance table in their respective section. Choose, roll, customize the result or interpret it to suit your character;}
  \item {Choose or discover the character's starting gear. Refer to the class description for starting equipment. Add personal flair or backstory elements to these items;}
  \item {Discover the character's skills. Each class grants specific skills. Note these abilities for gameplay;}
  \item {Discover or decide what the character was doing before they became an adventurer. This shouldn't be more than a paragraph;}
\end{enumerate}

subsection{Selecting a character class}
A PLAYER may select a character's class or use the following table to roll on a random class.
\begin{table}[h!]
\centering
\begin{tabular}{|c|l|}
\hline
\textbf{d6 Roll} & \textbf{Result} \\
\hline
1 & Chump \\
2 & Imagined \\
3 & Fighter \\
4 & Knave \\
5 & Mage \\
6 & Talking animal \\
\hline
\end{tabular}
\caption{d6 Table for Discovering a Character Class}
\label{tab:d6_character_table}
\end{table}

Each class has unique traits, abilities, and starting equipment:
\begin{itemize}
\textbf{Chump}: A hapless character with little skill but endless determination.
\textbf{Imagined}: A creature brought to life through imagination, artistry, and craftsmanship. Scarecrows, Galateas, and Frankenstein's Monsters all fit into this class.
\textbf{Fighter}: A skilled combatant with powerful weapons and armor.
\textbf{Knave}: A versatile adventurer who is always ready for anything.
\textbf{Mage}: A master of arcane arts with powerful spells.
\textbf{Talking animal}: A whimsical, mysterious creature capable of speech and unique talents.
\end{itemize}
