\section{Character Classes}
This chapter describes the six standard character classes in Neon Manifesto. Each class provides unique traits, skills, and equipment that define a character's role and capabilities in the game.

\subsection{Selecting a character class}
A PLAYER may select a character's class or use the following table to roll on a random class.
\begin{table}[h!]
\centering
\begin{tabular}{|c|l|}
\hline
\textbf{d6 Roll} & \textbf{Result} \\
\hline
1 & Chump \\
2 & Imagined \\
3 & Fighter \\
4 & Knave \\
5 & Mage \\
6 & Talking animal \\
\hline
\end{tabular}
\caption{d6 Table for Discovering a Character Class}
\label{tab:d6_character_table}
\end{table}

Each class has unique traits, abilities, and starting equipment:
\begin{itemize}
\item \textbf{Chump}: A hapless character with little skill but endless determination.
\item \textbf{Imagined}: A creature brought to life through imagination, artistry, and craftsmanship. Scarecrows, Galateas, and Frankenstein's Monsters all fit into this class.
\item \textbf{Fighter}: A skilled combatant with powerful weapons and armor.
\item \textbf{Knave}: A versatile adventurer who is always ready for anything.
\item \textbf{Mage}: A master of arcane arts with powerful spells.
\item \textbf{Talking animal}: A whimsical, mysterious creature capable of speech and unique talents.
\end{itemize}

\input{section/classes/chump}
\input{section/classes/fighter}
\input{section/classes/knave}
\input{section/classes/mage}
\input{section/classes/talking_animal}
\input{section/classes/crafted}
