\section{Adventuring Gear}
Each character has 8 burden slots, which they can use to carry gear. Inside of each slot there can be an item of gear or part of a larger item. This chapter describes adventuring gear in three distinct tiers: basic; advanced; and magic. The items described, however, are not an exhaustive list of every piece of gear that can exist in every Neon Manifesto game world, but a set of common and suggested gear with help on how to adjudicate each. PLAYERS and CONDUCTORS may add new pieces of gear to the game world, though it's up to the CONDUCTOR to classify gear between the three tiers.

In the world of Neon Manifesto, only merchants and the rich deal in coins. Acquiring gear can be done through actions in haven and demesne phases, as well as found or looted during adventures.

\subsection{Basic Gear}
\begin{multicols}{2}
\subsubsection*{Tools}
Tools relevant to a skill will add a +1 to standard rolls using the skill.

\subsubsection*{Weapons}
Weapons are required to make attacks using the relevant skill, and will work as tools providing +1 to standard rolls using their skill.

\subsubsection*{Two-handed or dual weapons}
Weapons that must be wielded in both hands. Fighters and Knaves wielding them add a d6 when attacking.

\subsubsection*{Shields}
Shields can be wielded if the character is not wielding two-handed or dual weapons. Shields have three uses, and can be used to nullify a hit, after which the shield breaks. A character -- except for example a large talking animal -- cannot carry more than one shield, as it's awkward to.

\subsubsection*{Oil}
If there is light, oil can be thrown at foes and ignited. This is an attack that always rolls 2d6. Oil can also be thrown on the floor to make a pool of fire that hits those who try passing through it once per round.

\subsubsection*{Holy water}
If there is light, holy water can be thrown at unoly enemies. This is an attack that always rolls 4d6.

\subsubsection*{Refreshments}
Fine long-lasting food, meats, cheeses and wines can be offered to underworld and wilderness denizens as coin and tribute.

\subsubsection*{Other basic gear}
Unlisted gear that doesn't require a lot of work, advanced (think renaissance) tecnology or magic to make is considered basic gear.

\end{multicols}

\subsection{Advanced Gear}
\begin{multicols}{2}
\subsubsection*{Effective medicine}
Can be consumed during rest in the underworld or wilderness to recover 1d6 HITs.

\subsubsection*{Metal Treasure}
Like refreshments, can be offered to underworld and wilderness denizens as coin and tribute. It can also be used to pay for the cost of projects, if the CONDUCTOR stipulates a cost.

\subsubsection*{Gems and Jewelry}
Like metal treasure, except six of these are required to take up a burden.

\end{multicols}

\subsection{Magic Gear}
\begin{multicols}{2}
\subsubsection*{Potion of Healing}
Can be consumed at any time to recover 1d6 HITs.

\subsubsection*{Potion of Extra Healing}
Can be consumed at any time to recover all lost HITs.

\end{multicols}