\newpage
\subsection{Chump}
The weakest class, a Chump is a commoner of the world, starting at level 0 and requiring a single EXPERIENCE to level up to 1. There is nothing inherently special about playing a Chump, other than the challenge, the excitement of being weak, and the drama potential it brings. When a Chump reaches level 1, they change their class.

\begin{multicols}{2}
\begin{itemize}
  \item \textbf{HIT VALUE}: 2
  \item \textbf{HITS}: 2
  \item \textbf{MAX BENNIES}: 2
\end{itemize}

\subsubsection*{Appearence}
Roll 1d6 or choose from the table below to determine your Chump's very ordinary appearance:

\begin{adjustbox}{width=0.45\columnwidth,center}
\begin{tabular}{|c|l|}
\hline
\textbf{d6} & \textbf{Appearance} \\
\hline
1 & Plain face \\
2 & Slightly pudgy \\
3 & Balding \\
4 & Calloused hands \\
5 & Nervous demeanor \\
6 & Easily overlooked \\
\hline
\end{tabular}
\end{adjustbox}

\subsubsection*{Starting Gear}
Chumps always start with a tool of their trade (determined by their starting skill) and a questionable trinket that might come in handy:

\begin{adjustbox}{width=0.95\columnwidth,center}
\begin{tabular}{|c|l|}
\hline
\textbf{d12} & \textbf{Questionable Trinket} \\
\hline
1 & A bent spoon that occasionally vibrates \\
2 & A small pouch of sand that always feels damp \\
3 & A rusty key that fits no known lock \\
4 & A wooden duck whistle that sounds like a chicken \\
5 & A pair of mismatched socks that never get dirty \\
6 & A compass that always points to the nearest tavern \\
7 & A pocket watch that runs backwards \\
8 & A small mirror that shows yesterday's reflection \\
9 & A tin of mints that taste like grass \\
10 & A quill pen that writes in invisible ink \\
11 & A miniature sundial that works indoors \\
12 & A mood ring that's perpetually stuck on "mildly annoyed" \\
\hline
\end{tabular}
\end{adjustbox}

\subsubsection*{Starting Skills}
Roll 1d12 on the table to determine your Chump's starting skills. You may also choose a line. Considering all of the first skills in every line is a specification of the Art/Craft skill, a Chump gets a +3 bonus to their standard rolls using those skill with their starting tool, and would roll 3d6 if they somehow manage to attack using the skill and the tool.

\begin{adjustbox}{width=0.75\columnwidth,center}
\begin{tabular}{|c|l|}
\hline
\textbf{d12} & \textbf{Skills} \\
\hline
1 & Farming 1, Strength 1 \\
2 & Carpentry 1, Manuality 1 \\
3 & Blacksmithing 1, Strength 1 \\
4 & Weaving 1, Manuality 1 \\
5 & Pottery 1, Manuality 1 \\
6 & Cooking 1, Calculus 1 \\
7 & Masonry 1, Strength 1 \\
8 & Leatherworking 1, Manuality 1 \\
9 & Brewing 1, Calculus 1 \\
10 & Tailoring 1, Manuality 1 \\
11 & Scribing 1, Languages 1 \\
12 & Animal Handling 1, Strength 1 \\
\hline
\end{tabular}
\end{adjustbox}

\subsubsection*{Class Change}
Once a Chump reaches level 1, they roll on the Class Change table instead of rolling for a talent. It's possible that a Chump that wasn't an animal or a creature of imagination becomes a Talking Animal or an Imagined. This is intentional. Chumps adopt the HIT VALUE, HITS and MAX BENNIES of their new class, keep their existing skills, and gain the new class's skills through the starting skills table. Their appearence can be changed through the new class' appearence table. They don't get the new class' starting gear.

\end{multicols}

\begin{table}[b!]
\centering
\begin{tabular}{|c|l|}
\hline
\textbf{d6 Roll} & \textbf{Result} \\
\hline
1 & Gain a new Chump starting skill set (by rolling at the table), then reroll \\
2 & Imagined \\
3 & Fighter \\
4 & Knave \\
5 & Mage \\
6 & Talking animal \\
\hline
\end{tabular}
\end{table}
