\newpage
\subsection{Knave}
The witty ministrel, the cunning rogue, the varlet in sour armor. Knaves are resourceful adventurers, relying on skill to outlive the competition.

\begin{multicols}{2}
\begin{itemize}
  \item \textbf{HIT VALUE}: 3
  \item \textbf{HITS}: 4
  \item \textbf{MAX BENNIES}: 7
\end{itemize}

\subsubsection*{Appearence}
Roll 1d6 or choose from the table below to determine your Knave's appearance:

\begin{adjustbox}{width=0.85\columnwidth,center}
\begin{tabular}{|c|l|}
\hline
\textbf{d6} & \textbf{Appearance} \\
\hline
1 & Flamboyant clothes \\
2 & Fit body \\
3 & Brooding and mysterious \\
4 & Vulpine grin \\
5 & Practical attire \\
6 & Ordinary (roll on the Chump appearence table)\\
\hline
\end{tabular}
\end{adjustbox}

\subsubsection*{Starting Gear}
Knaves always start with a weapon of choice (you choose what the weapon is), a set of tools for operating mechanisms and devices (e.g. lockpicks), a bundle of rope and other adventuring gear. Roll or choose on the table.

\subsubsection*{Starting Skills}
All Knaves start with Mechanisms and Devices 2. Roll or choose on the table, once for each column, to determine your Knave's starting skills.
\begin{adjustbox}{width=0.85\columnwidth,center}
\begin{tabularx}{\columnwidth}{|c|p{0.2\columnwidth}|p{0.2\columnwidth}|p{0.31\columnwidth}|}
\hline
\textbf{d6} & \textbf{Basic} & \textbf{Trade} & \textbf{Cunning} \\
\hline
1 & Awareness 2 & Weapon (choose) 2 & Script 3 \\
\hline
2 & Strength 2 & Languages 2 & Disguise 3 \\
\hline
3 & Calculus 2 & Healing 2 & Acrobatics 3 \\
\hline
4 & Rhetoric 2 & Evaluate 2 & Poison 3 \\
\hline
5 & Manuality 2 & Survival 2 & Art/Craft (music or dance) 3 \\
\hline
6 & Spell 2 & Art/Craft (choose) 2 & Choose another class' table to roll from, adding up redundant skills \\
\hline
\end{tabularx}
\end{adjustbox}

\subsubsection*{Knave's Craft}
Whenever a Knave rolls a 1, 2 or 3 on a die, they may spend a BENNY to reroll the die. This works even on light and supply rolls.

\end{multicols}

\begin{table}[!b]
    \centering
    \small
    \setlength{\extrarowheight}{-1pt}
    \newcolumntype{Y}{>{\raggedright\arraybackslash}X}
    \begin{tabularx}{\textwidth}{|c|Y|}
    \hline
    \textbf{2d6 Roll} & \textbf{Talent} \\
    \hline
    2 & \textbf{Skill and Luck:} Increase your maximum BENNIES by 2.\\
    \hline
    3-5 & \textbf{Stumble Forward:} When you fail to score a HIT in an attack roll. Gain an additional BENNY.\\
    \hline
    6 & \textbf{Reliable Knave:} Pick a skill, once per day you can choose to roll a six on a standard roll using the skill. You cannot choose the same skill for this talent. \\
    \hline
    7 & \textbf{Skill Focus:} Gain a SKILL BENNY (+3, standard rolls using a starting skill only). Recover it as you would regular BENNY. Max X SKILL BENNIES, where X is times you have this talent. \\
    \hline
    8 & \textbf{Flagrant Strike:} The first time you attack a target unaware of your presence and/or hostility in a combat, you roll an additional d6 \\
    \hline
    9-11 & \textbf{Knave's Vigor:} spend 6 BENNIES to recover a HIT at any time. Each time you take this talent reduce the BENNIES cost by 1\\
    \hline
    12 & \textbf{Multiknave:} Choose any other talent from any class table. \\
    \hline
    \end{tabularx}
    \end{table}

\begin{adjustbox}{width=\textwidth, center}
    \small
    \begin{tabularx}{\textwidth}{|c|p{0.2\textwidth}|X|}
    \hline
    \textbf{d12} & \textbf{Common Gear (roll or choose twice)} & \textbf{Oddities (roll once)} \\
    \hline
    1 & Grappling hook & A faithful steed \\
    \hline
    2 & Crowbar & \textbf{Book of Boredom}: Whoever tries reading it falls asleep after a minute \\
    \hline
    3 & 10-foot pole & \textbf{Vial of Spirits}: When drunk, puts the drinker's body into a coma. The drinker's spirit can roam freely, incorporeal, can speak but not attack. The effect lasts for a day.\\
    \hline
    4 & Oil flask & \textbf{Fiddle of Captivity}: When played in a haven or demesne, you become the main event. Everyone in the location can do nothing but attend and engage with your performance. Usable once a week.\\
    \hline
    5 & Wooden Stakes (10) & \textbf{Pipes of Hamelin}: If in a haven or in the underworld, a swarm of rats will assist you as long as you're playing it, and then they'll go away in peace\\
    \hline
    6 & Bundle of wolfsbane & \textbf{Immovable cat}: The cat is loyal to you and becomes immovable if tapped on the nose \\
    \hline
    7 & Holy water flask & \textbf{Potion of Flight}: Fly at your normal speed for a watch\\
    \hline
    8 & Caltrops & \textbf{Potion of Invisibility}: Become invisible for a watch or until an attack roll is made \\
    \hline
    9 & Ball bearings & \textbf{Potion of Gaseous Form}: Become a slow, intangible cloud for a watch \\
    \hline
    10 & Smoke bombs (3) & \textbf{Wishing Brandy}: Make a wish as you drink it. It comes true for a watch, then reality goes back to normal\\
    \hline
    11 & Forgery kit & \textbf{Amulet of Silence}: Once activated, nothing within a meter of the holder of this amulet can cause any sound at all\\
    \hline
    12 & Disguise kit & \textbf{Horn of the Herald}: When playing it, you can choose how far the horn is heard. Its maximum range spans the entire realm\\
    \hline
    \end{tabularx}
\end{adjustbox}